An assessment of photometric redshift PDF performance in the context of LSST

### 2018-11-16 paper/tex/appendix.tex
update appendix figures

\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{fig/ZPEAK_szpz_threecolumn_12codes_navy.jpg}\\
\includegraphics[width=0.8\textwidth]{fig/ZWEIGHT_szpz_threecolumn_12codes_navy.jpg}
\caption{Point estimate photo-z's derived from the posteriors. Top panel shows $z_{PEAK}$, while bottom panel shows $z_{WEIGHT}$.  Point estimate density is represented with fixed density contours, while outliers at lower density are represented by blue points.  While use of point-estimate photo-$z$'s is not recommended, they do make for useful comparative and visual diagnostics.  In the lower-right panel of each plot, the \trainz\ estimator results in identical photo-$z$ estimates at the mode and mean of the training set $N'(z)$ distribution for all galaxies.} \label{fig:pz_pointestimates}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{fig/ZPEAK_szpz_threecolumn_12codes_navy_lowalpha.jpg}\\
\includegraphics[width=0.8\textwidth]{fig/ZWEIGHT_szpz_threecolumn_12codes_navy_lowalpha.jpg}
\caption{Point estimate photo-z's derived from the posteriors. Top panel shows $z_{PEAK}$, while bottom panel shows $z_{WEIGHT}$.  Point estimate density is represented with fixed density contours, while outliers at lower density are represented by blue points.  While use of point-estimate photo-$z$'s is not recommended, they do make for useful comparative and visual diagnostics.  In the lower-right panel of each plot, the \trainz\ estimator results in identical photo-$z$ estimates at the mode and mean of the training set $N'(z)$ distribution for all galaxies.} \label{fig:pz_pointestimates}
\end{figure*}
